% !TEX root = ../main.tex

\section{Introduction}

Since the advent of the \faas model for Serverless computing in 2014  
by Amazon,
% \footnote{\url{https://aws.amazon.com/lambda/}}, 
all major cloud service providers, including 
Google,
% \footnote{\url{https://cloud.google.com/functions}}, 
Microsoft,
%\footnote{\url{https://azure.microsoft.com/services/functions/}}, 
and IBM,
%\footnote{\url{https://cloud.ibm.com/functions/}}
have introduced equivalent services. 
%
In addition to these offers, a growing number of open-source platforms 
such as Apache OpenWhisk,
%\footnote{\url{https://openwhisk.apache.org}}, 
OpenFaas,
%\footnote{ \url{https://www.openfaas.com}}, 
and Kubeless
%\footnote{\url{https://kubeless.io}} 
are being actively developed and maintained to support the \faas programming model.

In contrast to the traditional cloud offerings where users explicitly provision or configure 
backend services, in \faas, infrastructure management is left to the provider, enabling 
developers to focus on the application logic. 

To develop a Serverless application with the \faas model, programmers upload the code 
of one or more functions to the cloud and select the trigger events~(e.g., a REST request, 
a file upload) that activate the functions. The cloud provider is then responsible for 
deployment and resource provisioning. This eliminates the need for over-provisioning 
to ensure that peak resource requirements can be met.
Thus, the developers are charged only for the resources that the application actively requires.

Even though the \faas approach simplifies programmers' tasks, 
% by providing an environment to focus on developing applications in high-level languages, 
it also introduces several challenges.
 %for the development and performance of such applications. 
First, developers are forced to adopt a programming model that despite superficial 
similarities to the well known imperative and functional models,
significantly departs from them in practice.
% A number of aspects contribute to that.
For example, similar to functional programming, in the Serverless model, 
programs are required to be stateless
to enable autoscaling via automated function parallelization~\cite{hellerstein2018serverless}.
Yet, function composition, which is the cornerstone of functional programming,
is often considered an antipattern in Serverless computing~\cite{baldini2017serverless}.
%
Consequently, developers resort to a programming model that 
resembles the imperative model but presents fundamental 
differences -- including the fact that the state of a function is not 
preserved across several executions and
distinct functions that belong to the same application may not even execute 
on the same machine. As a result, it is a common solution 
to use external shared storage systems 
to save intermediate data across functions 
executions~\cite{klimovic2018understanding}.


Second, the performance and cost of Serverless applications are much harder to 
predict than traditional cloud applications. A number of aspects concur 
to this issue.
For example, one of the consequences of the common programming practice
of adopting an external storage system is that cross-function communication 
is slower and costlier than point-to-point networking.
Other issues are inherently due to the characteristics of Serverless systems,
including lack of information on data locality~\cite{DBLP:journals/corr/abs-1902-03383},
delays due to containers startup time~\cite{manner2018cold}, 
complex triggering processes~\cite{pelle2019towards}, and
limited lifetime of functions~\cite{hellerstein2018serverless}.

Third, we lack tool support for various aspects of
Serverless application development, including testing, debugging 
and continuous integration~\cite{lenarduzzi2020serverless,nupponen2020serverless}.
Like a small monolithic system, a function can be unit tested 
locally before deployment. 
However, system/integration testing and debugging can 
be more complex when more than a single function is involved. 
In a Serverless application with several functions, 
most function
% environmental 
dependencies are only available at runtime, 
making local integration testing and debugging impossible in 
some cases~\cite{leitner2019mixed}.


The issues above, exacerbated by the vendor lock-in that is currently 
characterizing vast amount of the Serverless computing market, 
pose the major challenges that slower the adoption of the \faas model. 

A first step to address these challenges is to achieve a 
better understanding of how the Serverless computing model is used in practice. 
Unfortunately, relatively little is known about the characteristics 
and the behavior of real-world Serverless applications. Existing studies focus 
on specific aspects, such as evolution of the Serverless vendors ~\cite{spillner2019quantitative} 
or performance of Serverless applications across different providers\cite{wang2018peeking,lloyd2018serverless},
but they do not provide a general-purpose dataset for research on Serverless computing.
Other researchers either applied research methodologies, 
such as developer interviews and literature surveys~\cite{leitner2019mixed},
or used small datasets containing only tens of applications~\cite{eismann2020serverless}.


In this work, we bridge this gap by providing a dataset of 1,877 real-world Serverless 
applications which is ready to use for researchers who are interested in investigating
Serverless applications. Our dataset, `\emph{Wonderless}', is publicly 
available\footnote{\url{https://drive.google.com/drive/folders/1I0yA0wqatcVhrVJuMq820tcrS9B7kGVF?usp=sharing}} 
and the source code\footnote{\url{https://github.com/allprojects/wonderless}} 
is open for replication as well as for extension.











